### 2014-03-30 trunk/paper_enahpc14/paper.tex
updates introduction and bibliography

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is a general template file for the LaTeX package SVJour3
% for Springer journals.          Springer Heidelberg 2010/09/16
%
% Copy it to a new file with a new name and use it as the basis
% for your article. Delete % signs as needed.
%
% This template includes a few options for different layouts and
% content for various journals. Please consult a previous issue of
% your journal as needed.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\RequirePackage{fix-cm}
%
\documentclass[twocolumn]{svjour3}           % twocolumn
%
\smartqed % flush right qed marks, e.g. at end of proof
%
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage[round, sort, numbers, authoryear]{natbib}
%
\DeclareRobustCommand\IPCClongname{}
%
% please place your own definitions here and don't use \def but
% \newcommand{}{}
%
% Insert the name of "your journal" with
% \journalname{myjournal}
%
\begin{document}

@@

\begin{abstract}
  In this paper we present  COSMO-ART, an extension of the operational
  weather  forecast  model  of   the  German  Weather  Service  (DWD),
  developed for  the evaluation of the interactions  of reactive gases
  and aerosol particles  with the state of atmosphere  at the regional
  scale. It  includes secondary aerosols,  directly emitted components
  like  soot,  mineral  dust,  sea  salt and  biological  material  as
  pollen. Processes such  as emissions, coagulation, condensation, dry
  deposition,  wet removal,  and sedimentation  of aerosols  are taken
  into account.   The overall performance  of this application  on HPC
  systems is  analysed by a  profiling and tracing study  to determine
  hotspots, i.e.  the  parts of the program that  require the dominant
  fraction of runtime, and to identify critical paths, i.e.  sequences
  of functions that shows dominant inclusive contributions for all its
  elements. Moreover, we describe measurement devices and energy-aware
  techniques  employed  to  evaluate   the  energy  footprint  of  the
  considered  application and  to  get detailed  insights about  power
  bottlenecks.   Our  motivation  is  to  improve  corresponding  code
  sections    to   sustain    high   performance    while   minimizing
  energy-to-solution.   This  preliminary  study  sets  the  basis  of
  broader  considerations  to  tackle  challenges  related  to  energy
  efficient   HPC  in   the   framework  of   the  Exa2Green   project
  (\url{http://exa2green.eu/}).

\keywords{High performance computing  \and Energy-aware computing \and
  Green computing  \and Numerical Weather  Prediction \and Atmospheric
  Chemistry \and Aerosol Modelling \and COSMO-ART}
% \PACS{PACS code1 \and PACS code2 \and more}
% \subclass{MSC code1 \and MSC code2 \and more}
\end{abstract}

@@

\section{COSMO-ART model description}
\label{sec:1}
\input{Sec1:COSMO-ART.tex}

\subsection{Subsection title}
\label{subsec:1}
Don't forget to  give each section and subsection  a unique label (see
Sect.~\ref{sec:1}).
\paragraph{Paragraph headings} Use paragraph headings as needed.
\begin{equation}
  a^2+b^2=c^2
\end{equation}

\begin{figure*}
  \includegraphics[width=0.4\textwidth]{Figs/earth.eps}
  \caption{Please write your figure caption here}
  \label{fig:1}
\end{figure*}

\begin{table}
  \caption{Please write your table caption here}
  \label{tab:1}
  \begin{tabular}{lll}
    \hline\noalign{\smallskip}
    first & second & third  \\
    \noalign{\smallskip}\hline\noalign{\smallskip}
    number & number & number \\
    number & number & number \\
    \noalign{\smallskip}\hline
  \end{tabular}
\end{table}

\begin{acknowledgements}
This  research  was  supported   by  the  Exa2Green  research  project
co-funded  under the  EU  7th Framework  Program  Future and  Emerging
Technologies (FET) Proactive Initiative: Minimising Energy Consumption
of Computing to  the Limit (MINECC).  The authors  would like to thank
the    High    Performance    and    High    Productivity    Computing
(\url{www.hp2c.ch}) Initiative.)
\end{acknowledgements}

\DeclareRobustCommand\IPCClongname{ Intergovernmental Panel on Climate Change}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is a general template file for the LaTeX package SVJour3
% for Springer journals.          Springer Heidelberg 2010/09/16
%
% Copy it to a new file with a new name and use it as the basis
% for your article. Delete % signs as needed.
%
% This template includes a few options for different layouts and
% content for various journals. Please consult a previous issue of
% your journal as needed.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\RequirePackage{fix-cm}
%
\documentclass[twocolumn]{svjour3}           % twocolumn
%
\smartqed % flush right qed marks, e.g. at end of proof
%
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage[round, sort&compress, numbers]{natbib}
%
\DeclareRobustCommand\IPCClongname{}
%
% please place your own definitions here and don't use \def but
% \newcommand{}{}
%
% Insert the name of "your journal" with
% \journalname{myjournal}
%
\begin{document}

@@

\begin{abstract}
  In this paper we present  COSMO-ART, an extension of the operational
  weather  forecast  model  of   the  German  Weather  Service  (DWD),
  developed for  the evaluation of the interactions  of reactive gases
  and aerosol particles  with the state of atmosphere  at the regional
  scale. It  includes secondary aerosols,  directly emitted components
  like  soot,  mineral  dust,  sea  salt and  biological  material  as
  pollen. Processes such  as emissions, coagulation, condensation, dry
  deposition,  wet removal,  and sedimentation  of aerosols  are taken
  into account.   The overall performance  of this application  on HPC
  systems is  analysed by a  profiling and tracing study  to determine
  hotspots  and  identify   critical  paths.   Moreover,  we  describe
  measurement devices and energy-aware techniques employed to evaluate
  the  energy  footprint of  the  considered  application  and to  get
  detailed  insights about  power bottlenecks.   Our motivation  is to
  improve  corresponding  code sections  to  sustain high  performance
  while  minimizing energy-to-solution.   This preliminary  study sets
  the basis of broader  considerations to tackle challenges related to
  energy efficient high performance  computing in the framework of the
  Exa2Green project (\url{http://exa2green.eu/}).

\keywords{High performance computing  \and Energy-aware computing \and
  Green computing  \and Numerical weather  prediction \and Atmospheric
  chemistry  \and  Aerosols  modelling  \and  Profiling  methods  \and
  Benchmark analysis \and COSMO-ART coupled model}
% \PACS{PACS code1 \and PACS code2 \and more}
% \subclass{MSC code1 \and MSC code2 \and more}
\end{abstract}

@@

\section{COSMO coupled with ART extension}
\label{sec:1}
\subsection{Model description and set-up}
\label{subsec:1}
\input{Sec1:COSMO-ART.tex}

\section{Hardware description}
\label{sec:2}

\section{Power measurement systems}
\label{sec:3}

\section{Benchmark results}
\label{sec:4}

%\paragraph{Paragraph headings} Use paragraph headings as needed.

%\begin{figure*}
%  \includegraphics[width=0.4\textwidth]{Figs/earth.eps}
%  \caption{Please write your figure caption here}
%  \label{fig:1}
%\end{figure*}

%\begin{table}
%  \caption{Please write your table caption here}
%  \label{tab:1}
%  \begin{tabular}{lll}
%    \hline\noalign{\smallskip}
%    first & second & third  \\
%    \noalign{\smallskip}\hline\noalign{\smallskip}
%    number & number & number \\
%    number & number & number \\
%    \noalign{\smallskip}\hline
%  \end{tabular}
%\end{table}

\begin{acknowledgements}
This  research  was  supported   by  the  Exa2Green  research  project
co-funded  under the  EU  7th Framework  Program  Future and  Emerging
Technologies (FET) Proactive Initiative: Minimising Energy Consumption
of Computing to  the Limit (MINECC).  The authors  would like to thank
the  High  Performance  and  High  Productivity  Computing  Initiative
(\url{www.hp2c.ch}).)
\end{acknowledgements}

\DeclareRobustCommand\IPCClongname{ - Intergovernmental Panel on Climate Change}
